---
title: "assignment_1"
author: "Morten Gade"
date: "3/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
# importing data and load packages

sleepstudy <- read.csv("sleepstudy.csv")
library(tidyverse)


```

## plot data

```{r}

ggplot(sleepstudy %>% group_by(Subject), aes(sleepstudy$Days, Reaction)) + 
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

ggplot(sleepstudy, aes(sleepstudy$Reaction)) + 
  geom_histogram()



```


## 1a

```{r}

subject_308 <- subset(sleepstudy, sleepstudy$Subject == 308)

lm_1 <- lm(subject_308$Reaction ~ subject_308$Days)

summary(lm_1)

#plot(sleepstudy)

```

The F-statistic is 17.12. The associated p-value is below the threshold of 0.05 suggesting a rejection of the null hypothesis. 

## 1b

The F-distribution takes in two parameters. The first degree of freedom equals the number of predictors, 1 in this case. The second df equals the number of data points minus number of predictors minus 1 (something to do with the mean), in this case 10-1-1 = 8. 

## 1c 

Initially the relevant F-distribution is plotted using the abovementioned degrees of freedom. 
Afterwards the cutoff-point is calculated using the quantile function. 


## 1d

```{r}
ggplot(subject_308, aes(Days, Reaction)) +
  geom_point() +
  geom_smooth(method = lm)
```

